---
title: "P8106_hw5_xh2395"
author: "Xin  He"
date: "5/9/2020"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ISLR)
library(caret)
library(e1071)
library(mlbench)
library(kernlab)
```

## Homework 5 Description

This problem involves the OJ data set which is part of the ISLR package. The data contains
1070 purchases where the customer either purchased Citrus Hill or Minute Maid Orange
Juice. A number of characteristics of the customer and product are recorded. Create a
training set containing a random sample of 800 observations, and a test set containing the
remaining observations.

## Import the data

```{r}
data(OJ)
oj_data = OJ %>% 
  janitor::clean_names()
```

## Create training data and test data

```{r}
set.seed(2020)
rowTrain = createDataPartition(y = oj_data$purchase,
                               p = 799/1070,
                               list = F)
train_data = oj_data[rowTrain, ]
test_data = oj_data[-rowTrain, ]
```

## a) Fit a support vector classifier (linear kernel)

```{r}
ctrl = trainControl(method = "cv")

set.seed(2020)

svml_fit = train(purchase ~ ., 
                  data = train_data, 
                  method = "svmLinear2",
                  preProcess = c("center", "scale"),
                  tuneGrid = data.frame(cost = exp(seq(-5,-1,len=50))),
                  trControl = ctrl)
```

### output

```{r}
svml_fit$finalModel

svml_fit$bestTune
```

### plot 

```{r}
ggplot(svml_fit, highlight = TRUE)
```

### training error rate

```{r}
pred_train = predict(svml_fit)
mean(train_data$purchase != pred_train)
```

The training error rate is 16.25%.

### test error rate

```{r}
pred_test = predict(svml_fit, newdata = test_data, type = "raw")
mean(test_data$purchase != pred_test)
```

The test error rate is 15.93%.

## b) Fit a support vector machine with a radial kernel

```{r}
svmr_grid = expand.grid(C = exp(seq(-5,2,len=20)),
                         sigma = exp(seq(-8,-1,len=10)))

set.seed(2020) 

svmr_fit = train(purchase ~ ., train_data,
                  method = "svmRadial",
                  preProcess = c("center", "scale"),
                  tuneGrid = svmr_grid,
                  trControl = ctrl)
```

### output

```{r}
svmr_fit$finalModel

svmr_fit$bestTune
```

### plot 

```{r}
ggplot(svmr_fit, highlight = TRUE)
```

### training error rate

```{r}
pred_train2 = predict(svmr_fit)
mean(train_data$purchase != pred_train2)
```

The training error rate is 16.88%.

### test error rate

```{r}
pred_test2 = predict(svmr_fit, newdata = test_data, type = "raw")
mean(test_data$purchase != pred_test2)
```

The test error rate is 16.30%.





